---
output:
  word_document:
    reference_docx: reference_doc.docx
  pdf_document: default
output_file: test_document.docx
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(dplyr)
library(stringr)
library(tidyr)
library(readr)
library(knitr)
library(kableExtra)
library(lubridate)
```

```{r get-files, echo=FALSE}
text_files <- list.files(path = ".", pattern = "\\.txt$", full.names = TRUE)

if (length(text_files) == 0) {
  message("No .txt files found in working directory.")
}

```

```{r reformat-functions, echo=FALSE}
reformat_in_development <- function(df) {

# ---- Defensive column creation ----
if (!"Expected publication date" %in% names(df)) {
df$`Expected publication date` <- NA_character_
}

if (!"Type" %in% names(df)) {
df$Type <- NA_character_
}

if (!"Link" %in% names(df)) {
df$Link <- NA_character_
}

if (!"Title" %in% names(df)) {
df$Title <- NA_character_
}

# ---- Begin transformations ----
df <- df %>%

# ---- Extract identifier from URL ----
# Examples:
# gid-ta11470 becomes GID-TA11470
# gid-qs10035 becomes GID-QS10035
# gid-mt12345 becomes GID-MT12345

mutate(
URL_ID = str_extract(
Link,
regex(
"gid-[a-z]+[0-9]+",
ignore_case = TRUE
)
)
) %>%

mutate(
URL_ID = str_to_upper(URL_ID)
) %>%

# ---- Remove existing IDs from the title ----
# Removes formats including:
# [GID-TA12010]
# GID-TA12010
# [ID6389]
# ID6389
# [TSID11810]
# TSID11810
# [TS ID 11810]
# TS ID 11810
# [MT12345]
# (MT12345)

mutate(
Title = str_remove_all(
Title,
regex(
paste0(
"\\s*",
"(",
"\\[(GID-[A-Z]+\\s*\\d+|TS\\s*ID\\s*\\d+|ID\\s*\\d+|MT\\s*\\d+)\\]",
"|",
"\\((MT\\s*\\d+)\\)",
"|",
"\\bGID-[A-Z]+\\s*\\d+\\b",
"|",
"\\bTS\\s*ID\\s*\\d+\\b",
"|",
"\\bID\\s*\\d+\\b",
")",
"\\s*"
),
ignore_case = TRUE
)
)
) %>%

# Remove extra spaces left behind after deleting IDs

mutate(
Title = str_squish(Title)
) %>%

# ---- Strip days from Expected publication date ----
# Retains the month and year only.

mutate(
`Expected publication date` =
str_remove_all(
`Expected publication date`,
"[:digit:][:digit:] |[:digit:] "
)
) %>%

# ---- Format the URL ----
# If the URL is present, put round brackets around it.
# If the URL is missing, flag the line for manual checking.

mutate(
Link = case_when(
!is.na(Link) & str_starts(Link, "\\(http") ~ Link,

!is.na(Link) & str_starts(Link, "http") ~
paste0("(", Link, ")"),

TRUE ~
" **MANUALLY CHECK THIS LINE AND THE ONE ABOVE**"
)
) %>%

# ---- Format the title ----
# Put square brackets around the title.

mutate(
Title = paste0("[", Title, "]")
) %>%

# Combine the title and its associated URL.
# This makes the title the clickable text.

unite(
Title,
Title,
Link,
sep = "",
na.rm = TRUE
) %>%

# ---- Normalise the guidance type ----

mutate(
Type = str_to_lower(Type)
) %>%

mutate(
Type = case_when(
is.na(Type) | Type == "" ~ "",

str_starts(Type, "nice") ~
str_replace(Type, "nice", ". NICE"),

TRUE ~
paste0(". NICE ", Type)
)
) %>%

# ---- Format the URL identifier ----
# Add a space before the identifier so it appears
# immediately after the guidance type.

mutate(
URL_ID = case_when(
!is.na(URL_ID) & URL_ID != "" ~
paste0(" ", URL_ID),

TRUE ~ ""
)
) %>%

# ---- Format Expected publication date text ----

mutate(
`Expected publication date` = case_when(
is.na(`Expected publication date`) |
str_trim(`Expected publication date`) == "" ~ "",

str_detect(
str_trim(`Expected publication date`),
regex(
"^(tbc|to be confirmed)$",
ignore_case = TRUE
)
) ~
". Publication date to be confirmed",

TRUE ~
paste0(
". Publication expected ",
str_trim(`Expected publication date`)
)
)
) %>%

# ---- Create final merged output ----

unite(
Merged,
Title,
Type,
URL_ID,
`Expected publication date`,
sep = "",
na.rm = TRUE
) %>%

select(Merged)

df
}


reformat_published <- function(df, Link, Title, `Reference number`, Published, `Last updated`, Merged) {
  df <- df %>%
  
# To create our titles with links this code: 
# Adds brackets to the start and end of the existing URLs,
# Adds square brackets to the titles
# Merges the two columns with unite.
  
  mutate(Link = str_replace(Link, "^", "(")) %>%
  mutate(Link = str_replace(Link, "$", ")")) %>%
  mutate(Title = str_replace(Title, "^", "[")) %>%
  mutate(Title = str_replace(Title, "$", "]")) %>%
  
      # Some entries are split across two rows for reasons that we don't understand. The next chunk of code is designed to identify these and add a note that they need manually checking.
    
mutate(
  Link = case_when(
    !is.na(Link) & str_starts(Link, "\\(http") ~ Link,
    !is.na(Link) & str_starts(Link, "http")   ~ paste0("(", Link, ")"),
    TRUE ~ " **MANUALLY CHECK THIS LINE AND THE ONE ABOVE**"
  )
) %>%    
    
  unite(Title, Title, Link, sep = "", na.rm=TRUE) %>%
    
# "NICE guideline NG/CG/QS/TA.." is added before the reference number 
# e.g. NG215 will become "NICE guideline NG215"
    
  mutate(`Reference number` = str_replace_all(`Reference number`, "^NG", "NICE guideline NG"))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^CG", "NICE guideline CG"))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^QS", "NICE quality standard "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^TA", "NICE technology appraisal guidance "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^IPG", "NICE interventional procedures guidance "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^DG", "NICE diagnostics guidance "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^HST", "NICE highly specialised technologies guidance "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^MTG", "NICE medical technologies guidance "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^MPG", "NICE medicines practice guideline "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^HTE", "NICE health technology evaluation "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^HTG", "NICE healthtech guidance "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^CSG", "NICE cancer service guideline "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^PH", "NICE guideline "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^SG", "NICE safe staffing guideline "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^SC", "NICE social care guideline "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^ES", "NICE evidence summary ES"))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^MIB", "NICE medtech innovation briefing "))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^ESNM", "NICE evidence summary ESNM"))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^ESUOM", "NICE evidence summary ESUOM"))%>%
  mutate(`Reference number` = str_replace_all(`Reference number`, "^ESMPB", "NICE evidence summary ESMPB"))%>%
    
# This code uses lubridate to reformat all the dates in the Published and Last Updated columns to display the year only 
  mutate(
SortDate = case_when(
!is.na(`Last updated`) &
str_trim(`Last updated`) != "" ~ dmy(`Last updated`),

TRUE ~ dmy(Published)
)
) %>%
  mutate(Published = format(dmy(Published),"%Y")) %>%
  mutate(`Last updated` = format(dmy(`Last updated`),"%Y")) %>%
  
# Create a column called Updated. 
    
# If the year in the Published column is equal to the year in the Last updated column, this will be blank.
    
# If the year is different to that in the Published column, the code will insert the word "updated" before the year. 
    
  mutate(Updated = case_when(
    Published == `Last updated` ~ "",
    TRUE ~ " last updated "))  %>%
  
  mutate(`Last updated`= case_when(
    `Last updated` != Published ~ paste("updated",`Last updated`, sep = " "),
    TRUE ~ ""))  %>%
  
# If the Last Updated column contains data (e.g. 'last updated 2023'), this code will paste the data across to the Published column in the format: 2020 last updated 2023.
    
  mutate(Published = case_when(
    `Last updated` != "" ~ paste(Published, `Last updated`, sep = " "),
    TRUE ~ Published))  %>%
  
# This code adds opening and closing brackets around data in the Published column. E.g. (Published 2020 last updated 2023)
    
  mutate(Published = str_replace(Published, "^", "(")) %>%
  mutate(Published = str_replace(Published, "$", ")"))  %>%
      
#Create a column called Merged. The code below will merge the Title, Published and Reference number into the new column. The merged data will be separated by a space in the new column. 
    
   mutate(Merged = "")  %>%
   unite(Merged, Merged, Title, Published, `Reference number`, sep = " ", na.rm=TRUE) 
}


reformat_deferred <- function(df) {

  df <- df %>%

      # Some entries are split across two rows for reasons that we don't understand. The next chunk of code is designed to identify these and add a note that they need manually checking.
    
mutate(
  Link = case_when(
    !is.na(Link) & str_starts(Link, "\\(http") ~ Link,
    !is.na(Link) & str_starts(Link, "http")   ~ paste0("(", Link, ")"),
    TRUE ~ " **MANUALLY CHECK THIS LINE AND THE ONE ABOVE**"
  )
) %>%  
    

mutate(
  Title = paste0("[", Title, "]")
) %>%
    unite(Title, Title, Link, sep = "", na.rm = TRUE) %>%

    # ---- Format Guidance programme to NICE style ----
    mutate(`Guidance programme` = str_to_lower(`Guidance programme`)) %>%
    mutate(`Guidance programme` = paste0(". NICE ", `Guidance programme`)) %>%

    # ---- Format Deferred ID ----
    mutate(`Deferred ID` = case_when(
      !is.na(`Deferred ID`) ~ paste0(" [ID", `Deferred ID`, "]"),
      TRUE ~ ""
    )) %>%

    # ---- Format Deferred date text ----
    mutate(`Deferred date` = case_when(
      is.na(`Deferred date`) | `Deferred date` == "" ~
        ". Publication date to be confirmed (deferred)",
      TRUE ~
        paste0(". Publication deferred – original date ", `Deferred date`)
    )) %>%

    # ---- Create final merged output ----
    unite(
      Merged,
      Title,
      `Guidance programme`,
      `Deferred ID`,
      `Deferred date`,
      sep = "",
      na.rm = TRUE
    ) %>%

    # ---- Return only what downstream code expects ----
    select(Merged)

  df
}


reformat_awaiting <- function(df) {

  # ---- Defensive column creation ----
  if (!"Title" %in% names(df)) {
    df$Title <- NA_character_
  }

  if (!"Type" %in% names(df)) {
    df$Type <- NA_character_
  }

  if (!"Link" %in% names(df)) {
    df$Link <- NA_character_
  }

  # ---- Begin transformations ----
  df <- df %>%

    # ---- Extract the identifier from the URL ----
    # Examples:
    # gid-ta11470 becomes GID-TA11470
    # gid-qs10035 becomes GID-QS10035
    # gid-ipg10331 becomes GID-IPG10331

    mutate(
      URL_ID = str_extract(
        Link,
        regex(
          "gid-[a-z]+[0-9]+",
          ignore_case = TRUE
        )
      )
    ) %>%

    mutate(
      URL_ID = str_to_upper(URL_ID)
    ) %>%

    # ---- Remove existing IDs from the title ----
    # Removes formats including:
    # [GID-TA12010]
    # GID-TA12010
    # [ID6389]
    # ID6389
    # [TSID11810]
    # TSID11810
    # [TS ID 11810]
    # TS ID 11810

    mutate(
      Title = str_remove_all(
        Title,
        regex(
          "\\s*\\[(?:GID-[A-Z]+\\d+|TS\\s*ID\\s*\\d+|ID\\s*\\d+)\\]\\s*|\\s*\\b(?:GID-[A-Z]+\\d+|TS\\s*ID\\s*\\d+|ID\\s*\\d+)\\b\\s*",
          ignore_case = TRUE
        )
      )
    ) %>%

    # Remove any extra spaces left after removing an ID

    mutate(
      Title = str_squish(Title)
    ) %>%

    # ---- Format the link ----
    # Adds round brackets around the URL.

    mutate(
      Link = case_when(
        !is.na(Link) & str_starts(Link, "\\(http") ~ Link,

        !is.na(Link) & str_starts(Link, "http") ~
          paste0("(", Link, ")"),

        TRUE ~
          " **MANUALLY CHECK THIS LINE AND THE ONE ABOVE**"
      )
    ) %>%

    # ---- Format the title ----
    # Adds square brackets around the title.

    mutate(
      Title = paste0("[", Title, "]")
    ) %>%

    # Combines the title and URL to create a clickable title.

    unite(
      Title,
      Title,
      Link,
      sep = "",
      na.rm = TRUE
    ) %>%

    # ---- Normalise guidance type ----

    mutate(
      Type = str_to_lower(Type)
    ) %>%

    mutate(
      Type = case_when(
        is.na(Type) | Type == "" ~ "",

        str_starts(Type, "nice") ~
          str_replace(Type, "nice", ". NICE"),

        TRUE ~
          paste0(". NICE ", Type)
      )
    ) %>%

# ---- Format URL identifier ----
# Adds a space before the identifier so that it follows
# the guidance type correctly.

mutate(
URL_ID = case_when(
!is.na(URL_ID) & URL_ID != "" ~
paste0(" ", URL_ID),

TRUE ~ ""
)
) %>%

# ---- Create final merged output ----

unite(
Merged,
Title,
Type,
URL_ID,
sep = "",
na.rm = TRUE
) %>%

select(Merged)

df
}

reformat_prioritisation <- function(df) {

# ---- Defensive column creation ----
if (!"Title" %in% names(df)) {
df$Title <- NA_character_
}

if (!"Link" %in% names(df)) {
df$Link <- NA_character_
}

if (!"Decision" %in% names(df)) {
if (ncol(df) >= 4) {
names(df)[4] <- "Decision"
} else {
df$Decision <- NA_character_
}
}

if (!"Decision date" %in% names(df)) {
df$`Decision date` <- NA_character_
}

# ---- Begin transformations ----
df <- df %>%

# ---- Extract identifier from URL ----
# Examples:
# gid-ta11470 becomes GID-TA11470
# gid-qs10035 becomes GID-QS10035
# gid-ipg10331 becomes GID-IPG10331

mutate(
URL_ID = str_extract(
Link,
regex(
"gid-[a-z]+[0-9]+",
ignore_case = TRUE
)
)
) %>%

mutate(
URL_ID = str_to_upper(URL_ID)
) %>%

# ---- Remove existing IDs from the title ----
# Removes formats including:
# [GID-TA12010]
# GID-TA12010
# [ID6389]
# ID6389
# [TSID11810]
# TSID11810
# [TS ID 11810]
# TS ID 11810

mutate(
Title = str_remove_all(
Title,
regex(
paste0(
"\\s*",
"(",
"\\[(GID-[A-Z]+\\s*\\d+|TS\\s*ID\\s*\\d+|ID\\s*\\d+)\\]",
"|",
"\\bGID-[A-Z]+\\s*\\d+\\b",
"|",
"\\bTS\\s*ID\\s*\\d+\\b",
"|",
"\\bID\\s*\\d+\\b",
")",
"\\s*"
),
ignore_case = TRUE
)
)
) %>%

# Remove extra spaces left after deleting IDs

mutate(
Title = str_squish(Title)
) %>%

# ---- Format the link ----

mutate(
Link = case_when(
!is.na(Link) & str_starts(Link, "\\(http") ~ Link,

!is.na(Link) & str_starts(Link, "http") ~
paste0("(", Link, ")"),

TRUE ~
" **MANUALLY CHECK THIS LINE AND THE ONE ABOVE**"
)
) %>%

# ---- Format the title ----

mutate(
Title = paste0("[", Title, "]")
) %>%

# Combine title and link so the cleaned title is clickable

unite(
Title,
Title,
Link,
sep = "",
na.rm = TRUE
) %>%

# ---- Format the URL identifier ----

mutate(
URL_ID = case_when(
!is.na(URL_ID) & URL_ID != "" ~
paste0(". ", URL_ID),

TRUE ~ ""
)
) %>%

# ---- Clean decision fields ----

mutate(
Decision = str_squish(Decision),
`Decision date` = str_squish(`Decision date`)
) %>%

# ---- Format decision text ----

mutate(
Decision = case_when(

# Blank decision
is.na(Decision) |
Decision == "" ~ "",

# Awaiting decision does not receive "Decision:"
str_detect(
Decision,
regex(
"^awaiting decision$",
ignore_case = TRUE
)
) ~
". Awaiting decision",

# All other decisions receive "Decision:"
TRUE ~
paste0(
". Decision: ",
str_to_sentence(Decision)
)
)
) %>%

# ---- Format decision date ----

mutate(
`Decision date` = case_when(

# Blank date
is.na(`Decision date`) |
`Decision date` == "" ~ "",

# Placeholder values are omitted completely
str_detect(
`Decision date`,
regex(
paste0(
"^(",
"tbc",
"|to be confirmed",
"|not yet confirmed",
"|not confirmed",
"|pending",
"|awaiting",
"|n/?a",
"|none",
"|unknown",
"|-",
"|–",
"|—",
")$"
),
ignore_case = TRUE
)
) ~ "",

# Valid date
TRUE ~
paste0(
". Decision date: ",
`Decision date`
)
)
) %>%

# ---- Create final merged output ----

unite(
Merged,
Title,
URL_ID,
Decision,
`Decision date`,
sep = "",
na.rm = TRUE
) %>%

select(Merged)

df
}

reformat_terminated <- function(df) {

  df <- df %>%

    # To create our titles with links this code:
    # Adds brackets to the start and end of the existing URLs,
    # Adds square brackets to the titles
    # Merges the two columns with unite.

    mutate(Link = str_replace(Link, "^", "(")) %>%
    mutate(Link = str_replace(Link, "$", ")")) %>%
    mutate(Title = str_replace(Title, "^", "[")) %>%
    mutate(Title = str_replace(Title, "$", "]")) %>%

    # Some entries are split across two rows for reasons that we don't understand.
    # The next chunk of code is designed to identify these and add a note that they need manually checking.

    mutate(
      Link = case_when(
        !is.na(Link) & str_starts(Link, "\\(http") ~ Link,
        !is.na(Link) & str_starts(Link, "http") ~ paste0("(", Link, ")"),
        TRUE ~ " **MANUALLY CHECK THIS LINE AND THE ONE ABOVE**"
      )
    ) %>%

    unite(Title, Title, Link, sep = "", na.rm = TRUE) %>%

    # "NICE guideline NG/CG/QS/TA.." is added before the reference number
    # e.g. NG215 will become "NICE guideline NG215"

    mutate(`Reference number` = str_replace_all(`Reference number`, "^NG", "NICE guideline NG")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^CG", "NICE guideline CG")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^QS", "NICE quality standard ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^TA", "NICE technology appraisal guidance ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^IPG", "NICE interventional procedures guidance ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^DG", "NICE diagnostics guidance ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^HST", "NICE highly specialised technologies guidance ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^MTG", "NICE medical technologies guidance ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^MPG", "NICE medicines practice guideline ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^HTE", "NICE health technology evaluation ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^HTG", "NICE healthtech guidance ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^CSG", "NICE cancer service guideline ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^PH", "NICE guideline ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^SG", "NICE safe staffing guideline ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^SC", "NICE social care guideline ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^ES", "NICE evidence summary ES")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^MIB", "NICE medtech innovation briefing ")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^ESNM", "NICE evidence summary ESNM")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^ESUOM", "NICE evidence summary ESUOM")) %>%
    mutate(`Reference number` = str_replace_all(`Reference number`, "^ESMPB", "NICE evidence summary ESMPB")) %>%

# Keep original terminated date

mutate(`Terminated date full` = `Terminated date`) %>%

# Create year from terminated date

mutate(`Terminated year` =
         format(dmy(`Terminated date`), "%Y")) %>%

# Put brackets around year

mutate(`Terminated year` =
         paste0("(", `Terminated year`, ")")) %>%

# Format full terminated date text

mutate(`Terminated date full` =
         paste0("Terminated date: ",
`Terminated date full`)) %>%

# Create final merged output

mutate(Merged = "") %>%

unite(
Merged,
Merged,
Title,
`Terminated year`,
`Reference number`,
sep = " ",
na.rm = TRUE
) %>%

mutate(
Merged = paste0(
Merged,
". ",
`Terminated date full`
)
)
}

```


```{r process-files, echo=FALSE}

published_list   <- list()
development_list <- list()
deferred_list    <- list()
awaiting_list    <- list()
prioritisation_list  <- list ()
terminated_list <- list()

for (f in text_files) {


df <- read_delim(
  f,
  delim = "\t",
  quote = "\\\"",
  escape_double = FALSE,
  trim_ws = TRUE
)

cols <- names(df)
if (is.null(cols)) cols <- character()

if ("Published" %in% cols) {

  published_list[[basename(f)]] <- reformat_published(df)

} else if ("Deferred date" %in% cols) {

  deferred_list[[basename(f)]] <- reformat_deferred(df)

} else if ("Terminated date" %in% cols) {

terminated_list[[basename(f)]] <- reformat_terminated(df)  
  
} else if (
"Decision date" %in% cols ||
"Decision" %in% cols
) {

prioritisation_list[[basename(f)]] <- reformat_prioritisation(df)

} else if (
  "Title" %in% cols &&
  "Type" %in% cols &&
  !"Expected publication date" %in% cols
) {

  awaiting_list[[basename(f)]] <- reformat_awaiting(df)

} else {

  # ✅ in development is the fallback
  development_list[[basename(f)]] <- reformat_in_development(df)

}

}
```

```{r bind-clean, echo=FALSE}
library(tibble)

# ----- Published -----

published_df <- bind_rows(published_list)

if (!"Merged" %in% names(published_df)) {
  published_df <- tibble(Merged = character())
} else {
  published_df <- published_df %>%
    filter(
      !is.na(Merged),
      str_trim(Merged) != ""
    ) %>%

    # Newest publication date first
    arrange(
      desc(SortDate),
      Merged
    ) %>%

    select(Merged)
}

# ----- In development -----
development_df <- bind_rows(development_list)

if (!"Merged" %in% names(development_df)) {
  development_df <- tibble(Merged = character())
} else {
  development_df <- development_df %>%
    filter(!is.na(Merged), str_trim(Merged) != "")
}

# ----- Deferred -----
deferred_df <- bind_rows(deferred_list)

if (!"Merged" %in% names(deferred_df)) {
  deferred_df <- tibble(Merged = character())
} else {
  deferred_df <- deferred_df %>%
    filter(!is.na(Merged), str_trim(Merged) != "")
}

# ----- Awaiting development -----
awaiting_df <- bind_rows(awaiting_list)

if (!"Merged" %in% names(awaiting_df)) {
  awaiting_df <- tibble(Merged = character())
} else {
  awaiting_df <- awaiting_df %>%
    filter(!is.na(Merged), str_trim(Merged) != "")
}

# ----- Topic prioritisation -----
prioritisation_df <- bind_rows(prioritisation_list)

if (!"Merged" %in% names(prioritisation_df)) {
  prioritisation_df <- tibble(Merged = character())
} else {
  prioritisation_df <- prioritisation_df %>%
    filter(!is.na(Merged), str_trim(Merged) != "")
}

# ----- Terminated -----
terminated_df <- bind_rows(terminated_list)

if (!"Merged" %in% names(terminated_df)) {
terminated_df <- tibble(Merged = character())
} else {
terminated_df <- terminated_df %>%
filter(
!is.na(Merged),
str_trim(Merged) != ""
) %>%
arrange(desc(dmy(`Terminated date`)))
}
```

## Published

```{r published, echo=FALSE, results='asis'}
if (nrow(published_df) > 0) {
  kable(published_df["Merged"], col.names = NULL)
} else {
  cat("Nothing found")
}
```

```{r spacer_after_published, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## Terminated

```{r terminated, echo=FALSE, results='asis'}
if (nrow(terminated_df) > 0) {
kable(
terminated_df["Merged"],
col.names = NULL
)
} else {
cat("Nothing found")
}
```

```{r spacer_after_terminated, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## In development

```{r development, echo=FALSE, results='asis'}
if (nrow(development_df) > 0) {
  kable(development_df["Merged"], col.names = NULL)
} else {
  cat("Nothing found")
}
```

```{r spacer_after_development, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## Suspended

*Open all 'In development' links created using the code after pasting into this scoping page to confirm whether the topic is still in development or is now suspended or discontinued. Where a topic is shown as suspended move to this section. Add a brief explanation of why the topic was suspended based on the information on the website.*

```{r spacer_after_suspended, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## Discontinued

*Where a topic is shown as discontinued move to this section. Add a brief explanation of why the topic was discontinued based on the information on the website.*

```{r spacer_after_discontinued, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## Awaiting development 

```{r awaiting, echo=FALSE, results='asis'}
if (nrow(awaiting_df) > 0) {
  kable(awaiting_df["Merged"], col.names = NULL)
} else {
  cat("Nothing found")
}
```

```{r spacer_after_awaiting, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## Deferred

```{r def, echo=FALSE, results='asis'}
if (nrow(deferred_df) > 0) {
  kable(deferred_df["Merged"], col.names = NULL)
} else {
  cat("Nothing found")
}
```

```{r spacer_after_def, echo=FALSE, results='asis'}
cat("\n\n\n")
```

## Topic prioritisation

```{r prioritisation, echo=FALSE, results='asis'}
if (nrow(prioritisation_df) > 0) {
  kable(prioritisation_df["Merged"], col.names = NULL)
} else {
  cat("Nothing found")
}
```

```{r ensure-dfs, echo=FALSE}
library(tibble)

if (!exists("published_df")) {
published_df <- tibble(Merged = character())
}

if (!exists("development_df")) {
development_df <- tibble(Merged = character())
}

if (!exists("deferred_df")) {
deferred_df <- tibble(Merged = character())
}

if (!exists("awaiting_df")) {
awaiting_df <- tibble(Merged = character())
}

if (!exists("prioritisation_df")) {
prioritisation_df <- tibble(Merged = character())
}

if (!exists("terminated_df")) {
terminated_df <- tibble(Merged = character())
}  

```



```{r cleanup, include=FALSE}

#Code to remove the exported text file from the working directory to prevent accidentally generating two identical bibliographies.

invisible(file.remove(text_files))
```
